ACNP 2024 MS ANXIETY

### 2024-08-13 scripts/MSAnxiety_manuscript_audrey_replication.Rmd
stats for promis - group too small

#anxiety_dose   0.3836     0.2391   1.605    0.114
anxiety_dose_x_diff_score <- lm(phys_mental_diff_score ~ anxiety_dose, df_for_promis_plot_mental_vs_physical_healthy_test)
summary(anxiety_dose_x_diff_score)
```

>>>>

#anxiety_dose   0.3836     0.2391   1.605    0.114
anxiety_dose_x_diff_score <- lm(phys_mental_diff_score ~ anxiety_dose, df_for_promis_plot_mental_vs_physical_healthy_test)
summary(anxiety_dose_x_diff_score)

#looking at anxiety_dose = 2 only, 0.22 -> sample size too small

mental_vs_physical_health_t <- t.test(df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired=F)
mental_vs_physical_health_t
```
